A Reduced Order Model for Porous Media Flows which Couples Linear Regression with Principal Component Analysis (PCA) using SVD or HOSVD: Upscaling the Permeability Field for Multiphase Reservoir Flow Simulation

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018.tex

\citet{AndrewNg_2018} was quoted to have said ``PCA is not linear regression, and despite some cosmetic similarity, these are actually totally different algorithms''. The main differences between these two mathematical methods is summarised in the Table~\ref{table:pca_vs_linreg} below and can also be deduced from the figure below.

@@

\red{I need to plot a figure here.}

>>>>

\citet{AndrewNg_2018} was quoted to have said ``PCA is not linear regression, and despite some cosmetic similarity, these are actually totally different algorithms''. The main differences between these two mathematical methods is summarised in the Table~\ref{table:pca_vs_linreg} below and can also be deduced from the figure~\ref{fig:PCA_is_not_LinReg}.

@@
